### 2023-04-18 paper.Rmd
minor

Note that when defining $\hat{x}_{tij}$, the condition $t = 1$ is separately included to keep the unchanged original data as the first $P$ columns in the data, which is used to equalize the the mean---the first moment---between groups.

Using the data matrix $\mathbf{\hat{X}}_{N \times \mathit{TP}}$ and a vector of weights $\mathbf{w} = (w_1, \dots, w_T$), the generalized multicriterion for k-plus anticlustering $\mathit{SSE_{kplusGeneralized}}$ can be formalized:

@@

Here, $w_t$ is the weight associated with the $t$'th moment, $\overline{x}_{tj} ^{(k)}$ is mean for the $k$'th group on the $j$'th $t$-moment variable. Maximizing $\mathit{SSE_{kplusGeneralized}}$ can be used to equalize the first $T$ distribution moments between $K$ groups.

>>>>

Note that when defining $\hat{x}_{tij}$, the condition $t = 1$ is separately included to keep the unchanged original data as the first $P$ columns in the data, which is used to equalize the the mean---the first moment---between groups. Using the data matrix $\mathbf{\hat{X}}_{N \times \mathit{TP}}$ and a vector of weights $\mathbf{w} = (w_1, \dots, w_T$), the generalized multicriterion for k-plus anticlustering $\mathit{SSE_{kplusGeneralized}}$ can be formalized:

@@

Here, $w_t$ is the weight associated with the $t$'th moment and $\overline{x}_{tj} ^{(k)}$ is mean for the $k$'th group on the $j$'th $t$-moment variable. Maximizing $\mathit{SSE_{kplusGeneralized}}$ can be used to equalize the first $T$ distribution moments between $K$ groups.
